%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Design of a broadband GaN Power Amplifier (currently working)} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {DC biasing, stability analysis, input/output matching is complete. Now working on load-pull, source-pull, harmonic balance analysis. Usng Cadance AWR.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Implementing Computational Methods to solve Maxwell's Equations} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Solved electrostatics problem using Method of Moment (MoM). Currently working on solving a electrostatics problem using FEM and an electrodynamics problem using FDTD. The computation was implemented in a combination of MATLAB, C++/Python code.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Design of a Reduced Footprint Wilkinson Power Divider with EMVerification} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Designed, simulated and optimized a Wilkinson Power Divider, working at 2.4GHz, in Keysight ADS. It was then transformed into a reduced-footprint design. Using generic DRC rule of ADS, EMVerification was done.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Design of a Five Pole Low Pass Filter with cut-off frequency of 2.4GHz and stop-band attenuation of -20dB at 5GHz.} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Designed, simulated and optimized a microwave LPF for the desired specification. Ansys HFSS was used.}
      \end{cvitems}
    }

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {Design of a Third Order 3dB Equal Ripple Low Pass Filter Using Microstrip Lines with a Cut-off Frequency of 4GHz.} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Designed, simulated and optimized a microwave LPF at $f_c=4$GHz. Ansys HFSS was used.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {16$\times$16 SRAM Array} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Designed (circuit level) and simulated a 6T $16\times16$ SRAM array. LTSpice XVII was used.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Matrix Multiplier - An Analog Approach} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {An approach to multiply two matrices where accuracy and precision can be within certain tolerance. Exploited the square-law current drawing characteristics of the class AB output stage of a BJT based OpAmps to multiply two numbers in-terms of normalized voltages. Then using proper summing amplifiers and voltage scaling amplifiers the final output is produced.}
        \item {\href{https://github.com/DhimanSarkar/BTech-Major-Project/raw/master/BTech Major Project/report.pdf}{Project Report Link.}}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {ELV-VLF Signal Receiver} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {An experimental setup for the study of atmospheric changes due to various causes like lightning, solar storm, eclipse, earthquake etc.}
        \item {https://github.com/DhimanSarkar/ELF-VLF-Signal-Receiver}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Precision Null Detector} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {An alternative to galvanometric implementations of analog null detector}
        \item{High precision and resolution than galvanometric implementations}
        \item {https://github.com/DhimanSarkar/Precision-Null-Detector}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Microphone Pre-amp} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {A general purpose op-amp based preamp implementation}
        \item {https://github.com/DhimanSarkar/Desktop\_Microphone\_PreAmp}
      \end{cvitems}
    }


%---------------------------------------------------------

  \cventry
    {Audio Amplifier Board} % Organisation
    {} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {24 watt output power • 4 input mixer • Bluetooth connectivity}
        \item {https://github.com/DhimanSarkar/Audio-Amplifier-System}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
